---
header-includes:
- \usepackage{booktabs}
- \usepackage{makecell}
output:
    pdf_document:
        latex_engine: xelatex
mainfont: LiberationSans
sansfont: LiberationSans
monofont: LiberationMono
params:
  data: NULL
  site: "KSL"
title: "AuTOMATIC Progress Report"
subtitle: "`r paste0('Clinic: ', paste0(params$site, collapse = ','))`"
date: "`r format(lubridate::today(), '%d %b %Y')`"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.height = 3,
	fig.width = 5
)
```


```{r pkgs}
library(tidyverse, warn.conflicts = FALSE)
library(lubridate, warn.conflicts = FALSE)
library(here, warn.conflicts = FALSE)
library(kableExtra, warn.conflicts = FALSE)

theme_set(theme_bw(base_size = 10))
```


```{r functions}
get_ordered_dat <- function(dat) {
  # Order the records to align the administration dates
  # Order is:
  #   - records with !NA date_of_vaccination_administration
  #   - date_of_vaccination_administration
  #   - date of record creation (redcap_dattim)
  #   - date of last modification (redcap_lastmod)
  dat_ordered <- dat %>%
    group_by(parent_id) %>%
    mutate(any_optout = ifelse(any(opted_out == 1, na.rm = T), 1, 0)) %>%
    group_by(parent_id, child_id) %>%
    mutate(n = max(row_number())) %>%
    arrange(parent_id, child_id, !is.na(date_of_vaccination_administration), date_of_vaccination_administration, redcap_dattim, redcap_lastmod) %>%
    mutate(vaxseq = cumsum(!is.na(current_eligible_vaccination))) %>%
    ungroup()
  return(dat_ordered)
}
```


```{r data}
data <- params$data
site <- params$site
dat <- data %>%
  dplyr::select(-redcap_repeat_instrument, -redcap_repeat_instance, -child_date_of_birth,
         -date_vaccine_due_clean, -date_vaccine_due_comment, -expected_date_sms_sent_clean,
         -expected_date_sms_sent_comment, -actual_date_sms_sent_clean, -actual_date_sms_sent_comment,
         date_of_vaccine_administration_clean, date_of_vaccine_administration_comment, -product_name_of_vaccine_administered,
         -smartvax_data_import_complete) %>%
  dplyr::filter(!(!is.na(date_vaccine_due) & date_vaccine_due <= as.Date("2021-01-10"))) # Exclude the incorrectly synchronised record which was prior to start-up
ordr_dat <- get_ordered_dat(dat)
site_dat <- ordr_dat %>% 
  filter(clinic_id %in% site)
```


```{r rand-dat}
# Number of parents randomised
n_rand_total <- length(unique(dat$parent_id))
n_rand <- length(unique(site_dat$parent_id))

# Date of randomisations (approximately)
d_rand <- site_dat %>%
  group_by(parent_id) %>%
  arrange(redcap_dattim) %>%
  filter(row_number() == 1) %>%
  select(parent_id, redcap_dattim) %>%
  ungroup() %>% 
  count(redcap_dattim = as_date(redcap_dattim)) %>%
  complete(redcap_dattim = seq(min(redcap_dattim), max(redcap_dattim), by = "1 day"), fill = list(n = 0)) %>%
  mutate(cn = cumsum(n))

# Number of total vaccination occasions (parent, child, age)
n_occasions <- site_dat %>% 
  count(parent_id, child_id, current_eligible_vaccination) %>% 
  filter(!is.na(current_eligible_vaccination)) %>%
  nrow()

site_summary <- tibble(Randomised = n_rand, `Due Vaccinations` = n_occasions)
```


```{r sms-dat}
# If a child gets vaccinated before the expected sms date,
# then no SMS will get set.
# If an SMS was sent, it was on or before the day of vaccination
# So only ever need to check the first record for each parent, child, age combination
sms_dat <- site_dat %>%
  group_by(parent_id, child_id) %>%
  mutate(
    # System perpetuates "actual_date_sms_sent" and "date_of_vaccination_administration" across new records
    # Need to clear these out.
    # "actual_date_sms_sent" is written to correct record, then perpetuates
    # "date_of_vaccination_administration" is written to subsequent (incorrect) record, then perpetuates
    actual_date_sms_sent = if_else(actual_date_sms_sent != lag(actual_date_sms_sent) | is.na(lag(actual_date_sms_sent)), actual_date_sms_sent, NA_Date_),
    vax_lead = lead(date_of_vaccination_administration, 1),
    vax_date = if_else(is.na(vax_lead), NA_Date_, 
                       if_else(vax_lead != date_of_vaccination_administration | is.na(date_of_vaccination_administration), 
                               vax_lead, NA_Date_))) %>%
  group_by(parent_id, child_id, current_eligible_vaccination) %>%
  filter(!is.na(current_eligible_vaccination)) %>%
  filter(row_number() == 1) %>%
  select(parent_id, child_id, current_eligible_vaccination, randomisation_outcome, clinic_id,
         expected_date_sms_sent, actual_date_sms_sent, sms_delivery_failure_indicator, vax_date) %>%
  ungroup()
sms_summary <- sms_dat %>%
  summarise(`SMS\nPlanned` = sum(!is.na(expected_date_sms_sent)),
            `SMS\nPast Due` = sum(expected_date_sms_sent < today() - 1, na.rm = T),
            `SMS\nSent`    = sum(expected_date_sms_sent < today() - 1 & !is.na(actual_date_sms_sent) & abs(actual_date_sms_sent - expected_date_sms_sent <= 1)),
            `SMS\nSuccess` = sum(expected_date_sms_sent < today() - 1 & abs(actual_date_sms_sent - expected_date_sms_sent <= 1) & sms_delivery_failure_indicator == "success", na.rm = T),
            `Vaccination\nbefore SMS` = sum(expected_date_sms_sent < today() - 1 & !is.na(expected_date_sms_sent) & vax_date < expected_date_sms_sent, na.rm = T))
# check <- sms_dat %>% filter((expected_date_sms_sent < today & !is.na(expected_date_sms_sent) & is.na(actual_date_sms_sent)))
# sms_dat %>% filter(randomisation_outcome != 1) %>% filter(expected_date_sms_sent < today - 1) %>% View
```


```{r vax-dat}
vax_dat <- site_dat %>%
  group_by(parent_id, child_id) %>%
    mutate(
      vax_lead = lead(date_of_vaccination_administration, 1),
      vax_date = if_else(is.na(vax_lead), NA_Date_, 
                         if_else(vax_lead != date_of_vaccination_administration | is.na(date_of_vaccination_administration), 
                                 vax_lead, NA_Date_))) %>%
  group_by(parent_id, child_id, current_eligible_vaccination) %>%
  filter(!is.na(current_eligible_vaccination)) %>%
  filter(row_number() == 1) %>%
  select(parent_id, child_id, current_eligible_vaccination, randomisation_outcome, clinic_id,
         expected_date_sms_sent, actual_date_sms_sent, sms_delivery_failure_indicator, date_vaccine_due, vax_date) %>%
  ungroup()
vax_summary <- vax_dat %>%
  summarise(
    `Vaccine\nPast Due` = sum(date_vaccine_due < today() - 1),
    `Vaccine\n28 days PD` = sum(date_vaccine_due < today() - 29),
    `Vaccine\nAdministered` = sum(date_vaccine_due < today() - 1 & !is.na(vax_date)),
    `Vaccine\n28 days PD\nAdministered` = sum(date_vaccine_due < today() - 29 & !is.na(vax_date))
  )
n_vax_pastdue <- vax_summary %>% pull(`Vaccine\nPast Due`)
n_vax_received <- vax_summary %>% pull(`Vaccine\nAdministered`)
n_sms_sent <- sms_summary %>% pull(`SMS\nSent`)
n_sms_planned <- sms_summary %>% pull(`SMS\nPlanned`)
```

\pagenumbering{gobble}

As of `r format(today(), "%d %b %Y")`, there have been `r n_rand_total` parents randomised at sites participating in AuTOMATIC.

At `r site`, `r n_rand` parents have been randomised.
<!-- Amongst participants randomised at `r site`, `r n_vax_pastdue` vaccinations are past due, and of these, `r n_vax_received` have been administered. -->
Amongst participants randomised at `r site`, `r n_sms_planned` SMS messages have been planned and `r n_sms_sent` of the planned messages have been sent.
SMS messages are not sent if the child is vaccinated prior to the planned message date.

```{r, rand-plot, fig.cap = paste0("Cumulative randomisations at ", paste0(site, collapse = ", "), ".")}
ggplot(d_rand, aes(redcap_dattim, cn)) +
  geom_step() +
  scale_y_continuous("Cumulative number of \nparents randomised", limits = c(0, NA)) +
  scale_x_date("Calendar date", date_breaks = "1 week", date_labels = "%d %b %Y") +
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5))
```


```{r sms}
tab <- bind_cols(site_summary, sms_summary)
colnames(tab) <- linebreak(colnames(tab), align = "c")
kable(tab, "latex", caption = paste0("Summary of planned and sent SMS at ", paste0(site, collapse = ", ")), 
      booktabs = TRUE, escape = FALSE) %>%
  kable_styling(latex_options = "hold_position")
```


```{r vax}
tab <- bind_cols(site_summary, vax_summary)
colnames(tab) <- linebreak(colnames(tab), align = "c")
kable(tab, "latex", caption = paste0("Summary of scheduled and administered vaccinations at ", paste0(site, collapse = ", ")), 
      booktabs = TRUE, escape = FALSE) %>%
  kable_styling(latex_options = "hold_position")
```
